### 2017-04-05 paper/evaluation.tex

To answer \numRQD{}, we considered all \numProjectsPar{} subjects from
our benchmark that use parallelization by default in Maven to run
tests.  Section~\ref{sec:rqC-1} describes in detail our methodology to
identify these subjects. For each project, the speedup (or slowdown)
corresponds to the ratio between the elapsed time of a sequential
execution and the elapsed time of a corresponding parallel execution,
obtained as described in the script from
Figure~\ref{fig:mvn-execution}.  As usual, a ratio above 1x denotes
speedup and a ratio below 1x denotes slowdown.

For each project, we modified the existing configurations to disable
the parallel test execution. In addition, we verified that both
executions produce the same outcome to eliminate noise from failing
tests.  To compute the speedup, we divide the time obtained in the
sequential execution by the time obtained from the default execution.
For instance, if a project runs the tests sequentially in $10m$ and
the same execution runs in $5m$ with parallelization enabled (default
execution), the speedup is two.

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{llrrl}
\toprule
Group & Subject & T$_{\text{d}}$ & T$_{\text{s}}$ & Speedup\\%
\midrule%
Medium & Jcabi GitHub & 0.30m & 2.75m & x9.01\\%
Medium & Apache Flink & 2.57m & 10.02m & x3.90\\%
Medium & Spotify Helios & 1.63m & 3.70m & x2.28\\%
Medium & Hazelcast Jet & 3.67m & 8.26m & x2.25\\%
  Long & Jenkins CI Gerrit Plugin & 40.31m & 76.32m & x1.89\\%
Medium & Jankotek MapDB & 8.58m & 10.51m & x1.23\\%
Medium & Javaslang & 1.82m & 2.12m & x1.16\\%
Medium & BounceStorage Chaos HTTP Proxy & 1.47m & 1.47m & x1.00\\%
Medium & Apache Log4J2 & 8.21m & 4.73m & x0.58\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Comparacao de tempo sequencial e paralelo ordenado por
    speedup}}
\label{tab:speedup}
\end{figure}

Figure~\ref{tab:speedup} summarizes our findings by increasing order
of speedup. The columns ``Group'' and ``Name'' indicates the time cost
group and the name of the subject, column ``T$_{\text{d}}$'' reports
the elapsed time in the default execution, the column
``T$_{\text{s}}$'' reports the elapsed time in the sequential
execution, and the column ``Speedup'' reports the overall speedup. We
observed that \Fix{falar sobre o resultado geral dos speedups -
elaborar menor e maior speedup... acho que so vale a pena discutir
quando tiver conviccao dos 2 casos}

>>>>

To answer \numRQD{}, we considered \emph{all} \numProjectsPar{}
subjects from our benchmark that use parallelization by default in
Maven to run tests.  Section~\ref{sec:rqC-1} describes in detail the
methodology we used to find these subjects. For each project, the
speedup (or slowdown) corresponds to the ratio ($T_s/T_p$) between the
elapsed time of a sequential execution ($T_s$) and the elapsed time of
a corresponding parallel execution ($T_p$), obtained as described in
the script from Figure~\ref{fig:mvn-execution}.  As usual, a ratio
above 1x denotes speedup and a ratio below 1x denotes slowdown.

%% For each project, we modified the existing configurations to disable
%% the parallel test execution. In addition, we verified that both
%% executions produce the same outcome to eliminate noise from failing
%% tests.  To compute the speedup, we divide the time obtained in the
%% sequential execution by the time obtained from the default execution.
%% For instance, if a project runs the tests sequentially in $10m$ and
%% the same execution runs in $5m$ with parallelization enabled (default
%% execution), the speedup is two.

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{llrrl}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.47m & 1.00x\\%
Medium & Apache \textbf{Flink} & 10.02m & 2.57m & 3.90x\\%
Long & Jenkins CI \textbf{Gerrit} Plugin & 76.32m & 40.31m &  1.89x\\%
Medium & Spotify \textbf{Helios} & 3.70m & 1.63m & 2.28x\\%  
Medium & \textbf{Javaslang} & 2.12m & 1.82m & 1.16x\\%
Medium & \textbf{Jcabi} GitHub & 2.75m & 0.30m & \cellcolor{lightgray}9.01x\\%
Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
Medium & Apache \textbf{Log4J2} & 4.73m & 8.21m & \cellcolor{lightgray}0.58x\\%
Medium & Jankotek \textbf{MapDB} & 10.51m & 8.58m & 1.23x\\%
\midrule
\textbf{total} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Abbreviation of project names appear in bold face
  and highest slowdown/speedup appear in gray color.}
\label{tab:speedup}
\end{figure}

Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
abbreviated project names, which appear in bold.  Columns
``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
project group and the name of the subject.  Column ``$T_s$'' shows
sequential execution time whereas column ``$T_p$'' shows parallel
execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
associated with parallel execution.

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
two extreme cases: \CodeIn{JCabi} and \CodeIn{Log4J2}.  \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}
